#b-SAT (with Grid)

This file is written to calculate b-SAT predictions for rho on a Linux machine.

The algorithm works by creating a grid of $x_{Bj}$ and $\mu$ values, evolving the gluon density using HOPPET for this finite number of values, then using the linear interpolation code in the <span style="color:blue;"><tt>Useful R Algorithms.Rmd</tt></span> (or <span style="color:blue;"><tt>.html</tt></span>) file to approximate values of $xg(x_{Bj},\ \mu)$ to use when integrating over $r$.

It was found that this code was not a good way of evolving the gluon density, since a fine enough grid could not be created. In order to have a grid with fine enough spacings, millions of evolutions would be required. Since one evolution takes approximately one second, it would take months to produce the grid. The problem is similar to that explained in <span style="color:blue;"><tt>bSAT - Trapezoidal Plots.Rmd</tt></span> (or <span style="color:blue;"><tt>.html</tt></span>).

##References and Libraries

```{r}

# References

# [1]: M. Ahmady, R. Sandapen, and N. Sharma, Phys. Rev. D 94, 074018 (2016), arXiv:1605.07665v2 [hep-ph].
# [2]: A. H. Rezaeian, and I. Schmidt, Phys. Rev. D 88, 074016 (2013), arXiv:1307.0825v3 [hep-ph].
# [3]: A. H. Rezaeian, et al., Phys. Rev. D 87, 034002 (2013), arXiv:1212.2974v1 [hep-ph].
# [4]: G. Watt, and H. Kowalski, Phys. Rev. D 78, 014016 (2008), arXiv:0712.2670v2 [hep-ph].
# [5]: S. A. Tehrani, and A. N. Khorramian, J. High Energy Phys. 0707:048 (2007), arXiv:0705.2647v2 [hep-ph].
# [6]: S. Bethke, G. Dissertori, and G. P. Salam, Quantum Chromodynamics (2015), PDG.

# References for experimental data

# [7]:  C. Adloff et al. (H1 Collaboration), Eur. Phys. J. C 13, 371 (2000).
# [8]:  F. D. Aaron et al. (H1 Collaboration), J. High Energy Phys. 05 (2010) 032.
# [9]:  S. Chekanov et al. (ZEUS Collaboration), Nucl. Phys. B718, 3 (2005), arXiv:hep-ex/0504010.
# [10]: S. Chekanov et al. (ZEUS Collaboration), PMC Phys. A 1, 6 (2007).

# Libraries

library(cubature) # For adaptIntegrate()
library(memoise)  # To cache variables using the memoise() function to make repeated calculations faster
library(compiler) # To compile functions using cmpfun() to make them faster
library(readxl)   # To import experimental data from excel spreadsheets

```

##Constants and Parameters

```{r}

# Define Bessel functions for shorthand

K = function (input) { besselK(input, 0) }
J = function (input) { besselJ(input, 0) }

# Constants

q_e        = sqrt(4*pi*(1/137)) # The elementary charge
kappa      = 0.54               # The mass scale
Lambda_QCD = 0.156              # For the coupling constant
N_c        = 3                  # The number of colours
n_f        = 4                  # The number of active flavours

# Equations (9.3) from Reference [6]

b_0 = (33 - 2*n_f)/(12*pi)                                  # The one-loop beta function coefficient
b_1 = (153 - 19*n_f)/(24*(pi**2))                           # The two-loop beta function coefficient
b_2 = (2857 - (5033/9)*n_f + (325/27)*n_f**2)/(128*(pi**3)) # The three-loop beta function coefficient

# b-SAT model parameters from Reference [3], Table 1

#                   A_g    lambda_g mu_nought   B_G C
bSAT_parameters = c(2.308, 0.058,   sqrt(1.51), 4,  4)

A_g       = bSAT_parameters[1]
lambda_g  = bSAT_parameters[2]
mu_nought = bSAT_parameters[3]
B_G       = bSAT_parameters[4]
bSAT_C    = bSAT_parameters[5]

# Meson-dependent constants (for phi)

M = 1.020
m = 0.14
e = 0.333333

```

##The Normalisation Constants

```{r}

# Longitudinal normalisation constant function

Normalise_L = function (variables) {
  
  # Integration variables
  
  x = variables[1]
  r = variables[2]
  
  # Wavefunctions from Equations (14) and (27) from Reference [1], simplified by hand
  
  exponent = exp((-1/2)*(((kappa**2)*(r**2)*x*(1 - x)) + ((m**2)/((kappa**2)*x*(1 - x)))))
  
  psi = sqrt(x*(1 - x))*exponent
  psi_dr2 = (kappa**2)*((x*(1 - x))**(3/2))*((kappa**2)*(r**2)*x*(1 - x) - 2)*exponent
  
  # Return the N_L integrand
  
  (1/2)*pi*r*((psi**2) + (2*(m**2)*(psi**2) - 2*psi*psi_dr2)/(x*(1 - x)*(M**2)) + ((m**4)*(psi**2) + (psi_dr2**2) - (2*(m**2)*psi*psi_dr2))/((x*(1 - x)*(M**2))**2))
  
}

# A function to calculate the transverse normalisation constant integrand

Normalise_T = function (variables) {
  
  # Integration variables
  
  x = variables[1]
  r = variables[2]
  
  # Wavefunctions from Equations (15) and (27) from Reference [1], simplified by hand
  
  exponent = exp((-1/2)*(((kappa**2)*x*(1 - x)*(r**2)) + ((m**2)/((kappa**2)*x*(1 - x)))))
  
  psi = sqrt(x*(1 - x))*exponent
  psi_dr = -((x*(1 - x))**(3/2))*(kappa**2)*r*exponent
  
  # Return the N_T integrand
  
  2*pi*r*(1/(4*(x**2)*((1 - x)**2)))*(((x**2 + (1 - x)**2)*(psi_dr**2)) + (m*psi)**2)
  
}

Normalise_L = cmpfun(Normalise_L)
Normalise_T = cmpfun(Normalise_T)

# Longitudinal and transverse normalisation constants
# The upper limits of 25 and 50 were chosen based on plots of Normalise_L() and Normalise_T() against x and r

N_L = 1/sqrt(adaptIntegrate(Normalise_L, lowerLimit = c(0, 0), upperLimit = c(1, 25))$integral)
N_T = 1/sqrt(adaptIntegrate(Normalise_T, lowerLimit = c(0, 0), upperLimit = c(1, 50))$integral)

```

##The PDF Grid

```{r, eval = FALSE}

# Set the working directory to /Codes/hoppet-1.2.0/example_f90
# This is so that data can be written to files in the correct folder for HOPPET to access

setwd("~/Codes/Hoppet/example_f90")

# Export the initial PDF parameters to a file called "parameters.txt"
# There is a line in HOPPET that reads these parameters in from this file

outfile = c(A_g, lambda_g)
write(outfile, file = "parameters.txt")

# Define the grid points in x and mu

x_grid  = seq(from = 0.0001, to = 0.02, by = 0.0001)
mu_grid = c(seq(mu_nought, 2, 0.01), seq(5, 50, 2))

# Export the x spacings into a file called "heralhc_xvals.txt"

write(x_grid, file = "heralhc_xvals.txt", ncolumns = length(x_grid))

# Declare a matrix to store the PDF that HOPPET will produce

pdf_grid = matrix(nrow = length(x_grid), ncol = length(mu_grid))

# Run HOPPET
# Do the evolution for all values of mu in mu_grid
# Store the PDF grid that HOPPET returns in pdf_grid

for (j in seq(1, length(mu_grid))) {
  
  mu = mu_grid[j]
  write(c(mu_nought, mu), file = "mu.txt")
  
  pdf_grid[, j] = as.numeric(system("./tabulation_example", intern = TRUE))
  
}

# The grid has now been created and filled
# The working directory has been automatically reset
# The grid can be used in the A_L() and A_T() functions by calling the pdf_grid matrix
# This part of the code does not have to be run again

```

##The Imaginary Scattering Amplitudes

```{r}

# Longitudinal imaginary scattering amplitude function

A_L = function(variables, x_Bj, Q2, t) {
  
  # Integration variables
  
  b = variables[1]
  x = variables[2]
  r = variables[3]
  
  # Equation (16) from Reference [3]
  # Define mu rather than mu2, because HOPPET evolves with mu
  
  mu = sqrt(bSAT_C/(r**2) + mu_nought**2)
  
  # Find the position i of the tabulated x value (in the grid) that the x value is closest to
  # Find the position j of the tabulated mu value (in the grid) that this mu value is closest to
  
  i = which.min(abs(x_grid - x_Bj))
  j = which.min(abs(mu_grid - mu))
  
  # Interpolate linearly between the grid points (i, j) and (i +/- 1, j)
  # Which points it uses depends on whether x_Bj is rounded up or down for the grid point approximation
  
  if (x_grid[i] - x_Bj < 0) {
    
    slope = (pdf_grid[i + 1, j] - pdf_grid[i, j])/(x_grid[i + 1] - x_grid[i])
    
  } else {
    
    slope = (pdf_grid[i - 1, j] - pdf_grid[i, j])/(x_grid[i - 1] - x_grid[i])
    
  }
  
  intercept = pdf_grid[i, j] - slope*x_grid[i]
  
  # Calculate the approximation of the evolved PDF value for this x and r
  
  xg = slope*x_grid[i] + intercept
  
  # Equation (9.5) from Reference [6]
  
  t_r = log((mu/Lambda_QCD)**2)
  alpha_s = (1/(b_0*t_r))
  
  # Variable-dependent equations
  
  epsilon = sqrt(x*(1 - x)*Q2 + m**2)           # Equation (8) from Reference [1]
  T_G     = (1/(2*pi*B_G))*exp(-(b**2)/(2*B_G)) # Equation (2.6) from Reference [3]
  
  # Equation (2.5) from Reference [3]
  
  N = 1 - exp(-(((pi**2)*(r**2))/(2*N_c))*(alpha_s * xg * T_G))
  
  # Wavefunctions from Equations (14) and (27) from Reference [1], simplified by hand
  
  exponent = exp((-1/2)*((kappa**2)*x*(1 - x)*r**2 + (m**2)/((kappa**2)*x*(1 - x))))
  
  psi     = sqrt(x*(1 - x))*exponent
  psi_dr2 = ((x*(1 - x))**(3/2))*(kappa**2)*((r**2)*(kappa**2)*x*(1 - x) - 2)*exponent
  
  # The photon and the vector meson wavefunctions
  
  psi_p = sqrt(N_c/pi)*q_e*e*x*(1 - x)*sqrt(Q2)*(K(epsilon*r)/pi)
  psi_V = (N_L/(2*sqrt(2)))*((1 + ((m**2)/(x*(1 - x)*(M**2))))*psi - (1/(x*(1 - x)*(M**2)))*psi_dr2)
  
  # Return the integrand for the longitudinal scattering amplitude
  
  2 *                     # Integrate x from 0 to 0.5
  psi_p *                 # The photon wavefunction
  psi_V *                 # The complex conjugate of the vector meson wavefunction
  2*N *                   # The dipole cross section
  2*pi*r*J(x*r*sqrt(t)) * # The r Bessel function
  2*pi*b*J(b*sqrt(t))     # The b Bessel function
  
}

# Transverse imaginary amplitude function

A_T = function(variables, x_Bj, Q2, t) {
  
  # Integration variables
  
  b = variables[1]
  x = variables[2]
  r = variables[3]
  
  # Equation (16) from Reference [3]
  # Define mu rather than mu2, because HOPPET evolves with mu
  
  mu = sqrt(bSAT_C/(r**2) + mu_nought**2)
  
  # Find the position i of the tabulated x value (in the grid) that the x value is closest to
  # Find the position j of the tabulated mu value (in the grid) that this mu value is closest to
  
  i = which.min(abs(x_grid - x_Bj))
  j = which.min(abs(mu_grid - mu))
  
  # Interpolate linearly between the grid points (i, j) and (i +/- 1, j)
  # Which points it uses depends on whether x_Bj is rounded up or down for the grid point approximation
  
  if (x_grid[i] - x_Bj < 0) {
    
    slope = (pdf_grid[i + 1, j] - pdf_grid[i, j])/(x_grid[i + 1] - x_grid[i])
    
  } else {
    
    slope = (pdf_grid[i - 1, j] - pdf_grid[i, j])/(x_grid[i - 1] - x_grid[i])
    
  }
  
  intercept = pdf_grid[i, j] - slope*x_grid[i]
  
  # Calculate the approximation of the evolved PDF value for this x and r
  
  xg = slope*x_grid[i] + intercept
  
  # Equation (9.5) from Reference [6]
  
  t_r = log((mu/Lambda_QCD)**2)
  alpha_s = (1/(b_0*t_r))
  
  # Variable-dependent equations
  
  epsilon = sqrt(x*(1 - x)*Q2 + m**2)           # Equation (8) from Reference [1]
  T_G     = (1/(2*pi*B_G))*exp(-(b**2)/(2*B_G)) # Equation (2.6) from Reference [3]
  
  # Equation (2.5) from Reference [3]
  
  N = 1 - exp(-(((pi**2)*(r**2))/(2*N_c))*(alpha_s * xg * T_G))
  
  # Wavefunctions from Equations (14) and (27) from Reference [1], simplified by hand
  
  exponent = exp((-1/2)*((kappa**2)*x*(1 - x)*r**2 + (m**2)/((kappa**2)*x*(1 - x))))
  
  psi = sqrt(x*(1 - x))*exponent
  psi_dr = -((x*(1 - x))**(3/2))*(kappa**2)*r*exponent
  
  # Product of the photon wavefunction and the complex conjugate of the vector meson wavefunction
  
  psi_Vp = N_T*sqrt(N_c/(2*pi))*q_e*e*((x**2 + (1 - x)**2)*(-epsilon*(besselK(epsilon*r, 1))/(2*pi))*(psi_dr/(2*x*(1 - x))) + (m**2)*(K(epsilon*r)/(2*pi))*(psi/(2*x*(1 - x))))
  
  # Return the integrand for the transverse scattering amplitude
  
  2 *                     # Integrate x from 0 to 0.5
  psi_Vp *                # The wavefunctions
  2*N *                   # The dipole cross section
  2*pi*r*J(x*r*sqrt(t)) * # The r Bessel function
  2*pi*b*J(b*sqrt(t))     # The b Bessel function
  
}

A_L = cmpfun(memoise(A_L))
A_T = cmpfun(memoise(A_T))

# Longitudinal imaginary scattering amplitude integration function

IntA_L = function (x_Bj, Q2, t) {
  
  adaptIntegrate(A_L, lowerLimit = c(1e-15, 1e-15, 1e-15), upperLimit = c(5, 0.5, 20), x_Bj, Q2, t, tol = 0.5)$integral
  
}

# Transverse imaginary scattering amplitude integration function

IntA_T = function (x_Bj, Q2, t) {
  
  adaptIntegrate(A_T, lowerLimit = c(1e-15, 1e-15, 1e-15), upperLimit = c(5, 0.5, 20), x_Bj, Q2, t, tol = 0.5)$integral
  
}

IntA_L = cmpfun(Vectorize(memoise(IntA_L)))
IntA_T = cmpfun(Vectorize(memoise(IntA_T)))

```

##The Differential Cross Sections

```{r}

# Longitudinal differential cross section function

d_sigma_L = function (t, Q2, W) {
  
  # Modified x_Bj for low Q2
  
  x_Bj = (Q2 + (M**2))/(Q2 + (W**2))
  
  # Real-part correction
  
  ImA_L_x = IntA_L(x_Bj, Q2, t)
  ImA_L_h = IntA_L(x_Bj + 1e-15, Q2, t)
  
  # Limit definition of the derivative of x_Bj
  
  alpha = -x_Bj*(1/(1e-15))*log(abs(ImA_L_x/ImA_L_h)) # Alternative form of Equation (13) from Reference [1]
  beta  = tan(pi*alpha/2)                             # Equation (13) from Reference [1]
  
  # Skewness term from Equation (14) from Reference [4]
  
  R_g = ((2**(2*alpha + 3))/(sqrt(pi)))*(gamma(alpha + (5/2))/gamma(alpha + 4))
  
  # Return the integrand for the longitudinal differential cross section
  
  (ImA_L_x**2) *              # Im(A_L) squared
  (1/(16*pi))*(1 + beta**2) * # Real-part correction
  ((R_g)**2) *                # Skewness term
  3.89379e5                   # Convert to nanobarns
  
}

# Transverse differential cross section function

d_sigma_T = function (t, Q2, W) {
  
  # Modified x_Bj for low Q2
  
  x_Bj = (Q2 + (M**2))/(Q2 + (W**2))
  
  # Real-part correction
  
  ImA_T_x = IntA_T(x_Bj, Q2, t)
  ImA_T_h = IntA_T(x_Bj + 1e-15, Q2, t)
  
  # Limit definition of the derivative of x_Bj
  
  alpha = -x_Bj*(1/(1e-15))*log(abs(ImA_T_x/ImA_T_h)) # Alternative form of Equation (13) from Reference [1]
  beta  = tan(pi*alpha/2)                             # Equation (13) from Reference [1]
  
  # Skewness term from Equation (14) from Reference [4]
  
  R_g = ((2**(2*alpha + 3))/(sqrt(pi)))*(gamma(alpha + (5/2))/gamma(alpha + 4))
  
  # Return the integrand for the transverse differential cross section
  
  (ImA_T_x**2) *              # Im(A_T) squared
  (1/(16*pi))*(1 + beta**2) * # Real-part correction
  ((R_g)**2) *                # Skewness term
  3.89379e5                   # Convert to nanobarns
  
}

d_sigma_L = cmpfun(Vectorize(memoise(d_sigma_L)))
d_sigma_T = cmpfun(Vectorize(memoise(d_sigma_T)))

```

##The Cross Section and Ratio

```{r}

# Cross section and ratio function

bSAT = function (Q2, W) {
  
  sigma_L = integrate(d_sigma_L, lower = 0, upper = 1, Q2, W, rel.tol = 0.1)$value
  sigma_T = integrate(d_sigma_T, lower = 0, upper = 1, Q2, W, rel.tol = 0.1)$value
	
  sigma = sigma_T + 0.98*sigma_L
  ratio = sigma_L/sigma_T
  
  # Return both values in a matrix
  # Use bSAT(Q2, W)[1,] for only sigma
  # Use bSAT(Q2, W)[2,] for only the ratio
  
  c(sigma, ratio)
  
}

bSAT = cmpfun(Vectorize(memoise(bSAT)))

```

##Theoretical Calculations

```{r, eval = FALSE}

start = Sys.time()

# Define the Q2 values at which to evaluate the cross section and ratio

bSAT_Q2 = 40.5

# Calculate the b-SAT predictions

bSAT_vs_Q2 = bSAT(bSAT_Q2, 75)

# Print how much time it took to do the computation

Sys.time() - start

```

```{r, eval = FALSE}

# Create vectors of CGC and b-CGC results to add to the plots
# These numbers were calculated using the Vector Meson Production.Rmd file
# They have been copied and pasted here so that those functions do not need to run

CGC_Q2 = c(2.5, 5, 6, 7, 10.5, 20, 25, 27.5, 30.5, 35, 40, 50, 75, 100)
bCGC_Q2 = c(2.5, 7.5, 30, 40, 50, 75, 100)

# Cross Section

CGC_sigma = c(533.88331042, 151.77546171, 103.53391327, 73.82881233, 28.19655142, 5.12731467, 2.68673139, 2.03137281, 1.47703014, 0.96427976, 0.63319957, 0.30579221, 0.07509027, 0.02572904)
bCGC_sigma = c(611.56972389, 70.91628992, 2.13251575, 0.94645563, 0.49791175, 0.14698466, 0.06311221)

# Ratio

CGC_ratio = c(1.182848, 1.775761, 1.979994, 2.162773, 2.744085, 4.044346, 4.698437, 4.956604, 5.310326, 5.774742, 6.373109, 7.210540, 9.176184, 10.464534)
bCGC_ratio = c(1.221070, 2.584364, 7.154170, 8.930552, 10.616710, 14.592281, 18.914043)

```

##Experimental Data

```{r, eval = FALSE}

# sigma vs Q2

# Reference [8], Table 14
H1_2010_rho_sigma = data.frame(read_excel("H1_2010_rho_sigma.xlsx", col_names = TRUE))

# Reference [10], Table 4
ZEUS_2007_rho_sigma = data.frame(read_excel("ZEUS_2007_rho_sigma.xlsx", col_names = TRUE))

```

```{r, eval = FALSE}

# ratio vs Q2

# Reference [7], Table 7
H1_2000_rho_ratio = data.frame(read_excel("H1_2000_rho_ratio.xlsx", col_names = TRUE))

# Reference [8], Table 49
H1_2010_rho_ratio = data.frame(read_excel("H1_2010_rho_ratio.xlsx", col_names = TRUE))

# Reference [10], Table 7
ZEUS_2007_rho_ratio = data.frame(read_excel("ZEUS_2007_rho_ratio.xlsx", col_names = TRUE))

```

##Cross Section Plot

```{r, eval = FALSE}

# sigma vs Q2

pdf("Rho - Cross Section vs Q2.pdf", width = 6*1.097542, height = 6)

# Create the plot

par(mai = c(1.05, 1.05, 0.45, 0.40))
plot(0, 1, pch = 21, col = "white", bg = "white", xlim = c(1, 100), ylim = c(0.01, 1000), xlab = "Q² [GeV²]", ylab = expression(sigma*" [nb]"), log = "y", axes = FALSE)

# Modify the plot features

box(bty = "o")
axis(1, at = c("0", "10", "20", "30", "40", "50", "60", "70", "80", "90", "100"))
axis(2, at = c("0.01", "0.1", "1", "10", "100", "1000"), labels = c("0.01", "0.1", "1", "10", "100", "1000"), las = 1)
legend(70.1, 1280, c("H1 (2010)", "ZEUS (2007)", "CGC", "b-CGC", "b-SAT"), lty = c(0, 0, 1, 2, 3), pch = c(17, 19, NA_integer_, NA_integer_, NA_integer_), col = c("red", "blue", "grey", "black", "red"), lwd = c(NA_integer_, NA_integer_, 4, 3, 5), bg = "white")

# Add theoretical data

lines(CGC_Q2, CGC_sigma, col = "grey", lty = 1, lwd = 4)
lines(bCGC_Q2, bCGC_sigma, col = "black", lty = 2, lwd = 3)
lines(bSAT_Q2, bSAT_vs_Q2_rho[1,], col = "red", lty = 3, lwd = 5)

# Add experimental data

points(H1_2010_rho_sigma$Q2, H1_2010_rho_sigma$sigma, pch = 24, col = "red", bg = "red")
points(ZEUS_2007_rho_sigma$Q2, ZEUS_2007_rho_sigma$sigma, pch = 21, col = "blue", bg = "blue")

# Add error bars

arrows(H1_2010_rho_sigma$Q2, H1_2010_rho_sigma$pos_error, H1_2010_rho_sigma$Q2, H1_2010_rho_sigma$neg_error, length = 0.04, angle = 90, code = 3, col = "red")
arrows(ZEUS_2007_rho_sigma$Q2, ZEUS_2007_rho_sigma$pos_error, ZEUS_2007_rho_sigma$Q2, ZEUS_2007_rho_sigma$neg_error, length = 0.04, angle = 90, code = 3, col = "blue")

```

##Ratio Plot

```{r, eval = FALSE}

# Ratio vs Q2

pdf("Rho - Ratio vs Q2.pdf", width = 6*1.097542, height = 6)

# Create the plot

par(mai = c(1.05, 1.05, 0.45, 0.40))
plot(0, 1, pch = 21, col = "white", bg = "white", xlim = c(1, 50), ylim = c(0.5, 12), xlab = "Q² [GeV²]", ylab = expression(sigma["L"]*" / "*sigma["T"]*""), axes = FALSE)

# Modify the plot features

box(bty = "o")
axis(1, at = c("0", "5", "10", "15", "20", "25", "30", "35", "40", "45", "50"))
axis(2, at = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12"), las = 1)
legend(1, 12, c("H1 (2000)", "H1 (2010)", "ZEUS (2007)", "CGC", "b-CGC", "b-SAT"), lty = c(0, 0, 0, 1, 2, 3), pch = c(15, 17, 19, NA_integer_, NA_integer_, NA_integer_), col = c("green", "red", "blue", "grey", "black", "red"), lwd = c(NA_integer_, NA_integer_, NA_integer_, 4, 3, 5), bg = "white")

# Add theoretical data

lines(CGC_Q2, CGC_ratio, col = "grey", lty = 1, lwd = 4)
lines(bCGC_Q2, bCGC_ratio, col = "black", lty = 2, lwd = 3)
lines(bSAT_Q2, bSAT_vs_Q2_rho[2,], col = "red", lty = 3, lwd = 5)

# Add experimental data

points(H1_2000_rho_ratio$Q2, H1_2000_rho_ratio$ratio, pch = 22, col = "green", bg = "green")
points(H1_2010_rho_ratio$Q2, H1_2010_rho_ratio$ratio, pch = 24, col = "red", bg = "red")
points(ZEUS_2007_rho_ratio$Q2, ZEUS_2007_rho_ratio$ratio, pch = 21, col = "blue", bg = "blue")

# Add error bars

arrows(H1_2000_rho_ratio$Q2, H1_2000_rho_ratio$pos_error, H1_2000_rho_ratio$Q2, H1_2000_rho_ratio$neg_error, length = 0.04, angle = 90, code = 3, col = "green")
arrows(H1_2010_rho_ratio$Q2, H1_2010_rho_ratio$pos_error, H1_2010_rho_ratio$Q2, H1_2010_rho_ratio$neg_error, length = 0.04, angle = 90, code = 3, col = "red")
arrows(ZEUS_2007_rho_ratio$Q2, ZEUS_2007_rho_ratio$pos_error, ZEUS_2007_rho_ratio$Q2, ZEUS_2007_rho_ratio$neg_error, length = 0.04, angle = 90, code = 3, col = "blue")

```